\documentclass[preprint,aps,pra,onecolumn]{revtex4-1} %reprint
%\tightenlines

%\draft
\usepackage{etex}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{bbm}
\usepackage{listings}
% % \textwidth 16cm \textheight 23.5cm
% \renewcommand{\baselinestretch}{1.2}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{color}
\usepackage{multirow}
\usepackage[colorlinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{calc}
\usepackage{natbib} %[numbers]
\usepackage{bibentry}
% underline tool
\usepackage[normalem]{ulem}
\usepackage{xcolor}
%\uline{foo}	Underlines foo
%\uuline{foo}	Double underlines foo
%\uwave{foo}	Underlines foo with a wavy line
%\sout{foo}	Strikesout foo
%\xout{foo}	Crosses out foo with ¡®/6¤7¡¯
% triple lines in colors
\makeatletter
\newcommand\uuuline{\bgroup\markoverwith%
   {%
     \textcolor{red}{\rule[-0.5ex]{2pt}{0.4pt}}%
     \llap{\textcolor{blue}{\rule[-0.7ex]{2pt}{0.4pt}}}%
     \llap{\textcolor{green}{\rule[-0.9ex]{2pt}{0.4pt}}}%
   }%
   \ULon}
\makeatother


\usepackage{amsmath,soul} % underline with a number
% usage example: $\underset{4}{\text{\ul{This is short text}}}$
% another package to use, but did not work for me.
% From: http://tex.stackexchange.com/questions/45341/labeling-underlined-text-over-multiple-lines
%\usepackage{soulpos}
%\ulposdef{\ulnumaux}{%
%   $\underset{\saveulnum}{\rule[-.7ex]{\ulwidth}{.4pt}}$}
%
%\newcommand{\ulnum}[2]{%
%  \def\saveulnum{#1}%
%  \ulnumaux{#2}}

% todo list and commands
\usepackage{todonotes}
%% to avoid the conflict with amths package % not working
%\makeatletter
%\providecommand\@dotsep{5}
%\makeatother
%\listoftodos\relax
\usepackage{makeidx}
\allowdisplaybreaks
% for eps transfering to pdf.
\usepackage[update,prepend]{epstopdf}
\usepackage{ifpdf}

\ifpdf
   \usepackage{graphicx}
   \usepackage{epstopdf}
   \epstopdfsetup{suffix=}
   \DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
   \pdfcompresslevel=9
\else
   \usepackage{graphicx}
\fi
% subfig
\usepackage{mwe}
\usepackage{subfig}
% to fix a figure's position using [H] option of thec figure.
\usepackage{float}
% to use \lesssim and other math symbols
\usepackage{amssymb}


% self-defined short-cuts and commands

% packages we need for judging the operating system
% compile your tex file with option -shell-escape is required: 
% e.g. xelatex -shell-escape file.tex
\usepackage{pdftexcmds}
\usepackage{catchfile}
\usepackage{ifluatex}
\usepackage{ifplatform}

\input{Mydef.tex}
% judge platform and include correct definiation package
%\ifwindows
%	%\input{F:/Research/Works/Templates/Mydef.tex} % %
%	\input{F:/Research/Works/Templates/Mydef.tex} % 
%\else
%	\input{/media/F/Research/Works/Templates/Mydef.tex} %
%\fi

%\includeonly{VectorTensor}
% for table captions.
\usepackage{tabularx,ragged2e,booktabs} %,caption

% packages for drawing
\usepackage{tikz}
%\usepackage{xypic}
%\usepackage[matrix,frame,arrow]{xypic}
\usetikzlibrary{calc}
%\input{Qcircuit}
\usepackage{qcircuit}

% Redefine the tensor command.
\renewcommand{\tensor}[1]{\boldsymbol{#1}}

\begin{document}
\title{Dispersive response: Phase shift and polarization transformation of guided nanofiber modes due to trapped atoms in the evanescent field (TBD)}
\author{}
\affiliation{CQuIC, UNM, Albuquerque, NM 87131, USA }
\date{\today}
%\pacs{42.50.Pq, 33.50.-j, 32.80.-t, 12.20.Ds}


\begin{abstract}
(TBD) Strong coupling between atoms and photons is a prerequisite for quantum information processing protocols ranging from quantum-limited metrology to quantum communication and computation.  This strong coupling regime can be achieved in a nanofiber platform whereby ensembles or atoms are trapped in a two-side chain through the evanescent field of a nanofiber.  In this work, we study the atom-photon interface in the dispersive regime, where the atoms' spin state is coupled to the photons' polarization through the index of refraction. We calculate this dispersive interaction through a first principles scattering model. Connections of the Green function method to a few other methods are discussed.  We calculate the dyadic Greens functions that allow and find the field scattered from the tensor-polarizable atoms. By decomposing the scattered field into guided and radiation modes, we study the phase shift and polarization rotation of the guided light along the nanofiber in presence of atoms. Compared with the free-space laser trapped atomic cloud systems, our results show that the nanofiber platform will yield strong coupling between the atoms and photons. We also analyzed the atomic state dependent phase shift and decay rates using a radiation surface model. We show the completely mixed state condition can also give a scalar polarizability effect to the phase shift. The interference effect due to a long one-sided or two-side atom chain is studied at the end of this work. This model will be used to design an efficient quantum data bus for entangling atoms with nanofiber modes.   
\end{abstract}

\maketitle

\section{Introduction}

\bigskip
\textcolor{blue}{Motivations: quantum data bus based on nanofiber trapped atomic systems; benefit from the advantages of the dispersive regime; connections to some existing theories; sensitivity of polarization spectroscopy...}




\section{Phase shift and polarization transformation of the guided modes of a nanofiber in presence of an atom}
The light-atom interaction Hamiltonian can be defined in terms of the atomic angular momentum operator $\hat{\mathbf{F}}$ and the photonic Stokes vector operator $ \hat{\mathbf{S}}$. In general, the evolution operator can be given by
\begin{align}
\hat{U}(\tau)&=e^{i\chi \mathbin{\color{red}{\hat{\mathbf{S}}}} \cdot \hat{\mathbf{F}}}.
\end{align}
For instance, if we only consider the Faraday rotation case that the Stokes operator only has the $\hat{S}_3$ component, and the initial state of the atom-light system is given by
\begin{align}
\ket{\Psi(0)} &=\frac{1}{\sqrt{2}}(\ket{\uparrow}+\ket{\downarrow})\mathbin{\color{red}{\ket{\phi_L}}}
\end{align}
where the atom is prepared in a superposition of spin up and down state, and the light in prepared in an arbitrary $\ket{\phi_L}$ state. The output after the Faraday interaction of duration $\tau$ will become
\begin{align}
\ket{\Psi(\tau)}&=\frac{1}{\sqrt{2}}\left[\ket{\uparrow}e^{+i\chi \mathbin{\color{red}{\hat{S}_3}}}\mathbin{\color{red}{\ket{\phi_L}}} 
+\ket{\downarrow}e^{-i\chi \mathbin{\color{red}{\hat{S}_3}}}\mathbin{\color{red}{\ket{\phi_L}}} \right]\\
&=\frac{1}{\sqrt{2}}\left[\ket{\uparrow}\mathbin{\color{red}{\ket{\phi^1_L}}} 
+\ket{\downarrow}\mathbin{\color{red}{\ket{\phi^2_L}}} \right]
\end{align}
The polarization of the light has been rotated along the $z$-axis, either $+2\chi$ or $ -2\chi$ around the $S_3$ axis on the Poincare sphere entangled with the spin state. Now the state of the joined system is in an entangled state between the spin system and the light. The entanglement between the atomic system and the light can be employed for quantum metrology and quantum information processing. 

The Faraday effect does not change the helicity of the polarized light. In general, however, the output Stokes vector $\mathbf{S}_{out}$ can be an arbitrary rotation along the three Poincare sphere axis after the atom-light interaction:
\begin{align}
\mathbf{S}_{out} &= \mathbf{S}_{in}+\mathbf{\Theta}\times\mathbf{S}_{in},
\end{align}
where the rotation angle along the $i$-axis is $\Theta_i \propto N_A\left( \frac{\sigma_0}{A}\right) \left(\frac{\Gamma}{2\Delta}\right)$ with effective atom number $N_A$, on-resonance scattering cross section $\sigma_0$, effective mode area $A$ which is inversely proportional to the mode square of the normalized electric field, atomic decay rate $\Gamma$ and the detuning $\Delta$. The rotation along the $S_1$ or $S_2$ axes yields the birefringence effect for the light. 

\textcolor{red}{Maybe a figure to show the Poincare sphere and the Faraday/birefringence effects here.}

For a given detuning and atom species, the effective atom number, $N_A$, and the optical depth per atom, $ OD=\sigma_0/A$, determines the rotation angle and hence the coupling strength between the joint systems. There have been a huge amount of efforts to enhance the atom-light interaction strength using the atom trapping configuration in free-space or vacuum~[\textcolor{red}{Refs}]. The problem for the vacuum trapping configuration is that the effective atom number $N_A$ is positively correlated with the effective mode area, and hence the total optical depth, $N_A\left( \frac{\sigma_0}{A}\right)$, is limited to some finite value around $50\sim 100$, typically with $10^6$ atoms. The nanofiber trapped atomic system, however, decouples the correlation between the effective atom number and the effective mode area. Each atom has the same amount of effective mode area, and experiences the same strength of field. Moreover, the evanescent probing field of the nanofiber where the atoms are trapped can be very strong compared to the vacuum trapping configuration due to the weak confinement of the nanofiber with a sub-wavelength diameter. With about $2000$ atoms, it is possible to achieve a total optical depth of $200$ as will be shown later. All of these factors above makes the nanofiber a promising platform for atom-light interfaces with strong coupling strength. 


In the consequent sections, we will firstly employ the Green function method to solve the semi-classical radiation and scattering problem of a two-level dipole in the evanescent field of a nanofiber. Then we will extend to the real atom in a quantized field case. The phase shift and birefringence effects will be studied in terms of orthogonal field components. For example, if the input field is diagonally linearly polarized as
\begin{align}
\mathbf{E}_{in} &= E_0(\hat{e}_x+\hat{e}_y),
\end{align}
the output field can be written as
\begin{align}
\mathbf{E}_{out} &= E_0(t_xe^{i\phi_x}\hat{e}_x+t_ye^{i\phi_y}\hat{e}_y).
\end{align}
The ratio of the attenuation coefficients, $t_x$ and $t_y$, indicates the helicity of the polarization of the light. $\phi_x$ and $\phi_y$ represent the phase shifts in the $x$- and $y$-modes. We will consider the phase shift for one input mode first, and then present our theory for the birefringence effect with two orthogonal input modes. 

\subsection{Nanofiber mode scattering due to an atom using the dyadic Green function method}
\textcolor{blue}{Start from the Maxwell equation with a dipole source and the corresponding equation of the dyadic Green function. Describe the framework of solving the fiber fields in presence of an atom using the dyadic Green function method.}

\textcolor{blue}{Sketch out the \textit{reflection-transmission decomposition} approach to solve the dyadic Green functions for the boundary value problem, and how to distinguish the radiation and guided modes through separating different integral paths. Detailed solutions should be given in the appendix. For the guided mode contribution to the dyadic Green function, give the explicit expression using the eigenmode decomposition method and make a clear link to the field quantization result. }

The Maxwell equation with dipole sources:
\begin{align}\label{eq:Maxwellwithsource2}
\left[\! -\! \nabla\!\!\times\!\nabla\!\!\times + n^2\!(\br)\frac{\omega^2}{c^2} \right]\!\! \boldsymbol{\mathcal{E}}(\br) &\!=\! -4\pi\! \frac{\omega^2}{c^2}\! \boldsymbol{\chi}(\br)\! \cdot\! \boldsymbol{\mathcal{E}}(\br)=\!-4\pi\! \frac{\omega^2}{c^2}\!\sum_{\br'}\delta(\br-\br')\boldsymbol{\alpha} \, (\br')\cdot \boldsymbol{\mathcal{E}}(\br).
\end{align}
The corresponding Green function for one dipole source satisfies
\begin{align}
\left[ -\nabla\times\nabla\times + n^2\frac{\omega^2}{c^2} \right] \mathbf{G}(\br,\br') &= \mathbf{I}\delta(\mathbf{r}-\mathbf{r}'). 
\end{align}
Each column can be expressed as
\begin{align}\label{eq:GFcolumneq}
\left[ -\nabla\times\nabla\times + n^2\frac{\omega^2}{c^2} \right] \mathbf{G}_i(\mathbf{r},\mathbf{r}') &= \mathbf{e}_i\delta(\mathbf{r}-\mathbf{r}'), 
\end{align}
where the subscription $ i=r\!_\perp,\phi,z $ denotes the coordinate components. Compared with Equ.~\ref{eq:Maxwellwithsource2}, one can find that each column of the dyadic function is equivalent to the electric filed solution in Equ.~\ref{eq:Maxwellwithsource2} with a dipole source of $-\frac{\mathbf{e}_i}{4\pi k^2}$. Therefore, one can solve the dyadic Green function by solving the radiation problem from a dipole source satisfying the boundary condition of the nanofiber.

Once we obtain the dyadic Green function of the nanofiber system, the total electric field with an input field $\mathbf{E}_0(\br)$ and in presence of a dipole source $\mathbf{d}(\br')$ positioned at $\br'$ can be given by
\begin{align}
\mathbf{E}(\br) &= \mathbf{E}_0(\br)-4\pi k^2\mathbf{G}(\br,\br')\cdot \mathbf{d}(\br')\\
&=\mathbf{E}_0(\br)-4\pi k^2 \mathbf{G}(\br,\br')\cdot \boldsymbol{\alpha}\cdot \mathbf{E}(\br')\\
&=\mathbf{E}_0(\br)-4\pi k^2 \mathbf{G}(\br,\br')\cdot \boldsymbol{\alpha}\cdot \mathbf{E}_0(\br').
\end{align}
The Born approximation has been used in the last step, which should be a good approximation for the far-detuning case we are interested in. 

For our problem, we only care about the guided mode contributions which are the dominate components detected at the end of a long nanofiber (a few centimeters long). One can show that the dyadic Green function for the guided modes can be written as \textcolor{red}{(Check the factor of 2 from this equation.)}
\begin{align}
\mathbf{G}_g(\br,\br') = -\frac{i\mathbin{\color{blue}{n_g}}}{4k_0} \sum_{m,f=\pm 1} \mathbf{u}_{\mu}(r\!_\perp)\mathbf{u}^*_{\mu}(r_{\!\perp}^\prime)e^{if\beta_0(z-z')+im(\phi-\phi')}.
\end{align}
In the equation above, the transverse modes of the nanofiber, $\mathbf{u}_{\mu}(\br)$, are defined by
\begin{align}
[-\nabla\times\nabla + \frac{\omega_{\mu}^2}{c^2}n^2(\br)]  \mathbf{u}_{\mu}(\br) &=0,
\end{align}
where the mode index $\mu=(\beta_0,m,f)$ with angular moment quantum number $ m $ and propagation index $ f $. We have used the circularly polarized modes as the basis for the eigenmode expansion for the dyadic Green function. One should be able to expand the dyadic Green functions in terms of any orthonormal basis, and replace the $m$ index with any other polarization indices. 

To retrieve the formula for the phase shift of an input mode in presence of a dipole, we consider the input field is
\begin{align}
\mathbf{E}_0(\br) &= E_0 \mathbf{u}_{m=1}^{f=1} (\br) = E_0 \mathbf{u}_1^1 (\mathbf{r}\!_\perp)e^{i\phi+i\beta_0 z}. 
\end{align}
The output can be retrieved as
$\mathbf{E}(\br)  = \mathbf{E}_0(\br) -4\pi k_0^2 \alpha \mathbf{G}^g(\br,\br')\cdot\mathbf{E}_0(\br')$.
The output field can also be expanded as
\begin{align}
\mathbf{E}(\br) &= E_0\mathbf{u}_{1}^{1} (\br) + \sum_{m,f=\pm 1} C_{mf} E_0 \mathbf{u}_m^f(\br),  
\end{align}
where the mode projection coefficients are
\begin{align}
C_{mf} &= -4\pi k_0^2 \alpha \!\int\! \mathrm{d}^2r\!_\perp n^2(\mathbf{r}\!_\perp){\mathbf{u}^f_m}^*(\mathbf{r})\cdot \mathbf{G}^g(\br,\br') \!\cdot\! \mathbf{u}_1^1(\mathbf{r}^\prime).
\end{align}
Using the eigenmode expansion of the dyadic Green function, these coefficients become
\begin{align}
C_{mf} &= i\pi k_0 n_g\alpha \!\int\! \mathrm{d}^2r\!_\perp n^2 {\mathbf{u}^f_m}^*(\mathbf{r}\!_\perp)\cdot\!\!\!\!\!\! \sum_{f',m'=\pm 1}\!\!\!\! \left[\mathbf{u}_{m'}^{f'}(\mathbf{r}\!_\perp){\mathbf{u}^{f'}_{m'}}^*(\mathbf{r}^\prime\!_\perp) \right]\!\cdot\! \mathbf{u}_1^1(\mathbf{r}^\prime\!_\perp)\nonumber\\
&\quad\quad\quad e^{if'\beta_0(z-z')} e^{i\beta_0(z'-fz)}\\
&= i\pi k_0 n_g\alpha  {\mathbf{u}^f_m}^*(r'_{\!\perp})\cdot \mathbf{u}_1^1(r'_{\!\perp})e^{i\beta_0 (1-f)z'+i(1-m)\phi'},
\end{align}
where the orthogonality relationship of the fiber modes had been used:
\begin{align}
\int n^2(\br)  \mathbf{u}_{\mathbf{k}}(\br) \cdot \mathbf{u}^*_{\mathbf{k}'}(\br)\mathrm{d} \br\!_\perp &=\delta_{\mathbf{k}\mathbf{k}'}\\
\Leftrightarrow \int_0^{2\pi}\!\!\!\!\! \mathrm{d}\phi\!\! \int_0^\infty\!\!\!\! r\!_\perp \mathrm{d}r\!_\perp  n^2(r\!_\perp) \mathbf{u}_{m}(r\!_\perp )\!\cdot\!\mathbf{u}_{m'}^*(r\!_\perp )& e^{i(f\!-\!f')\beta z+i(m\! -\! m')\phi}  =\delta_{mm'}e^{i(f\!-\!f')\beta z} \label{eq:orthutrans}.
\end{align}

The output forwarding $ m=1 $ HE11 mode component is then given by
\begin{align}
\mathbf{E}_+(\br) &= (1+C_{11})E_0\mathbf{u}_{1}^{1} (\br)\\
&\approx \exp\left[i\pi k_0 n_g\alpha  | \mathbf{u}_1^1(r'_{\!\perp})|^2 \right] E_0\mathbf{u}_{1}^{1} (\br)\\
&= \mathbin{\color{red}{te^{i\delta\phi}}}E_{in}(\br), 
\end{align}
where the factor change of the mode's amplitude is 
\begin{align}
t=\exp\left[\mathrm{Im}[C_{11}]\right]=\exp\left[ -\pi k_0 n_g \mathrm{Im}[\alpha]  | \mathbf{u}_1^1(r'_{\!\perp})|^2 \right]
\end{align}
and the phase shift is
\begin{align}
\delta\phi &= \mathrm{Re}[C_{11}]= \pi \mathrm{Re}[\alpha] \frac{\omega_0}{v_g}  | \mathbf{u}_1^1(r'_{\!\perp})|^2
= \pi \mathrm{Re}[\alpha] \frac{\omega_0}{cA^{11}_{e\!f\!f}},
\end{align}
where $ A^{mf}_{e\!f\!f}=1/n_g| \mathbf{u}_m^f(r'_{\!\perp})|^2 $ is the effective $(m,f)$ mode area at the atom position. 

We use the fact that 
\begin{align}
\alpha &=-\frac{|d_{eg}|^2}{\hbar \Delta}, \,\, (\Delta=\omega_{\beta}-\omega_{eg})\\
\Gamma^{1D}_{mf} &= 2\pi \frac{|d_{eg}|^2}{\hbar A^{mf}_{e\!f\!f}}\left(\frac{\omega_0}{v_g} \right)\\
\Gamma_{vac} &= \frac{4}{3} \left( \frac{\omega_0}{c}\right)^3 \frac{|d_{eg}|^2}{\hbar}\\
\sigma_0 &= \frac{3\lambda^2}{2\pi} \equiv \text{resonant cross section}
\end{align}
the phase shift can be rewritten as
\begin{align}
\mathbin{\color{red}{\delta\phi}} &= -\frac{\Gamma^{1\!D}_{11}}{2\Delta} = - \frac{\sigma_0 }{A'_{e\!f\!f}} \frac{\Gamma_{vac}}{8\Delta} = -\frac{c}{v_g} \sigma_0 |\mathbf{u}_1^1 (r'_{\!\perp})|^2 \frac{\Gamma_{vac}}{8\Delta}.
\end{align}

If there are two input modes, the Faraday and birefringence effects can be analyzed along this line. 

\subsection{Enhancement compared to the vacuum case}
Notice that, the phase shift for an atom in vacuum can be given in a similar form by
\begin{align}
\delta\phi^{vac} &= 2\pi \frac{\omega_0}{cA} \Re[\alpha] |\mathbf{u}_{00}(\br')|^2 =  2\pi \frac{\omega_0}{c A^{vac'}_{e\!f\!f}} \Re[\alpha]=-\frac{1}{A} \sigma_0 |\mathbf{u}_{00} (r'_{\!\perp})|^2 \frac{\Gamma_{vac}}{4\Delta},
\end{align}
where $\mathbf{u}_{00}(\br')  $ is the TEM00 mode of a Gaussian laser field at the atom position, $ A=\frac{\pi W_0^2}{2} $ is the mode area of the Gaussian beam with wist $ W_0 $. Hence, the relative strength of phase shift due to the presence of a nanofiber versus vacuum can be given by
\begin{align}
\frac{\delta\phi^{nano}}{\delta\phi^{vac}} &=\frac{A_{e\!f\!f}^{vac'}}{A_{e\!f\!f}^{11}}= \frac{A}{2} \!n_g\! \frac{|\mathbf{u}_1(r_\perp^{nano'})|^2}{|\mathbf{u}_{00}(r_\perp^{vac'})|^2}.
\end{align}
In the vacuum case, the strongest mode is given by $ |\mathbf{u}_{00}(r_\perp^{vac'})|=1 $ when the atom is placed at the center of the beam waist. 

\textcolor{red}{Figure for the enhancement comparison.}



\subsection{Quantum interface for the nanofiber with clock state}
We consider the case that the atoms are pumped to the clock state. Therefore, we only care about the atomic polarizability components
\begin{align}
\tensor{\alpha}_{\uparrow} &=\bra{f=4,m=0}\tensor{\alpha}\ket{f=4,m=0}\\
\tensor{\alpha}_{\downarrow} &=\bra{f=3,m=0}\tensor{\alpha}\ket{f=3,m=0}.
\end{align}
Suppose there are $H$ and $V$ two orthogonal linear polarized mode components. The quantized electric field can be given by
\begin{align}
\hat{\mathbf{E}}^{(+)}(r\!_\perp,\phi,z) &= \sqrt{ \frac{2 \pi \hbar \omega_0}{ v_g \tau} } \big( \mathbf{u}_H(r\!_\perp,\phi) \hat{a}_H + \mathbf{u}_V(r\!_\perp,\phi) \hat{a}_V \big) e^{i \beta z}.
\end{align}
The Hamiltonian can be given by
\begin{align}
H_{\rm eff}   &= -\hat{\mathbf{E}}^{(-)}(r^\prime\!\!_\perp,\phi',z')\cdot \tensor{\alpha}\cdot \hat{\mathbf{E}}^{(+)}(r^\prime\!\!_\perp,\phi',z')\\
 &=- \sum_{f,f'}\alpha_0(\Delta_{f,f'}) \left\{ C_{j'ff}^{(0)} \hat{\mathbf{E}}^{(-)} \cdot \hat{\mathbf{E}}^{(+)} \hat{\mathbbm{1}}_f \phantom{\frac{\hat{1}}{1}}\right. \nonumber\\
&\quad\quad\quad + i C_{j'ff'}^{(1)} \left(\hat{\mathbf{E}}^{(-)} \times \hat{\mathbf{E}}^{(+)} \right) \cdot \hat{ \mathbf{f}} \nonumber\\
&\quad\quad\quad  \left. + C_{j'ff}^{(2)} \hat{E}_i^{(-)} \hat{E}_j^{(+)} \left( \frac{ \hat{f}_i \hat{f}_j  + \hat{f}_j \hat{f}_i  }{2} - \frac{1}{3}\delta_{ij} \hat{ \mathbf{f}} \cdot \hat{\mathbf{f}}  \right) \right\}. 
\end{align}
The characteristic polarizability is given by
\begin{align} \label{Eq::alpha0}
\alpha_0(\Delta) & =  -\frac{|  \bra{ j' }| d | \ket{ j } |^2}{\hbar \Delta } = - \frac{3 \lambda_{j' j}^3}{32 \pi^3} \frac{ \Gamma }{ \Delta }\quad \text{with}\quad 
\Gamma = \frac{1}{\hbar} \frac{4}{3} \frac{\omega_{j j'}^3}{c^3} | \bra{ j' }| d | \ket{ j } |^2.
\end{align}
In our case, the vector component of the atomic polarizability is zero. We can ignore the tensor component of the atomic polarizability in the far off-resonance regime. The scalar polarizability coefficient is given by
\begin{align} \label{Eq::alpha0}
C_{j' f}^{(0)} &\equiv \sum_{f'} C_{j' f f'}^{(0)} =   \frac{2^{j'-1/2}}{3} =\left\{ \frac{1}{3},\frac{2}{3}\right\}.
\end{align}
The two values are for the D1 line and D2 line respectively.

The Hamiltonian can be rewritten as
\begin{align}
H_{\rm eff} & = \frac{ \hbar }{ \tau}\Big( \chi_{H,\uparrow}\op{\uparrow}{\uparrow} +  \chi_{H,\downarrow} \op{\downarrow}{\downarrow} \Big) \hat{a}_H\dg \hat{a}_H \nonumber\\
&\quad +  \frac{ \hbar }{ \tau} \Big( \chi_{V,\uparrow}\op{\uparrow}{\uparrow} +  \chi_{V,\downarrow} \op{\downarrow}{\downarrow} \Big) \hat{a}_V\dg \hat{a}_V  ,
\end{align}
where the coupling strengths are defined as
\begin{align}
\chi_{H,\uparrow} &=  -\frac{2\pi\omega_0}{v_g} \mathbf{u}^*_{H}(r^\prime\!\!_\perp,\phi') \cdot\tensor{\alpha}_{\uparrow}\cdot \mathbf{u}_{H}(r^\prime\!\!_\perp,\phi') \\
\chi_{H,\downarrow} &=  -\frac{2\pi\omega_0}{v_g} \mathbf{u}^*_{H}(r^\prime\!\!_\perp,\phi') \cdot\tensor{\alpha}_{\downarrow}\cdot \mathbf{u}_{H}(r^\prime\!\!_\perp,\phi') \\
\chi_{V,\uparrow} &=  -\frac{2\pi\omega_0}{v_g}  \mathbf{u}^*_{V}(r^\prime\!\!_\perp,\phi') \cdot\tensor{\alpha}_{\uparrow}\cdot \mathbf{u}_{V}(r^\prime\!\!_\perp,\phi')  \\
\chi_{V,\downarrow} &=  -\frac{2\pi\omega_0}{v_g}  \mathbf{u}^*_{V}(r^\prime\!\!_\perp,\phi') \cdot\tensor{\alpha}_{\downarrow}\cdot \mathbf{u}_{V}(r^\prime\!\!_\perp,\phi'). 
\end{align}
with $\tensor{\alpha}_{\uparrow} \approx\sum_{f'=3,4}\frac{\alpha_0(\Delta_{4,f'})}{3}\mathbf{I}$
and $\tensor{\alpha}_{\downarrow} \approx\sum_{f'=3,4}\frac{\alpha_0(\Delta_{3,f'})}{3}\mathbf{I}$.
One can use different detuning regime to detect the psuedo-spin state.

The coupling strength for the $ D_1 $ line probing can then be written as
\begin{align}
\chi_{H,\uparrow} &=  \sum_{f'} \frac{\chi_{H0}(f',4)}{3}, \quad
&\chi_{H,\downarrow} = \sum_{f'} \frac{\chi_{H0}(f',3) }{3}, \\
\chi_{V,\uparrow} &=  \sum_{f'} \frac{\chi_{V0}(f',4)}{3}, \quad
&\chi_{V,\downarrow} = \sum_{f'} \frac{\chi_{V0}(f',3) }{3} 
\end{align}
and 
\begin{align}
\chi_{H0}(f',f) &= \left( \frac{ \sigma_0}{A_{ef\!f}^H} \right) \left( \frac{\Gamma}{4 \Delta_{f,f'}} \right)=\frac{\Gamma_H^{1D}}{\Delta_{f,f'}},\quad
& A_{ef\!f}^H = \frac{1}{n_g|\mathbf{u}_{H}(r^\prime\!\!_\perp,\phi')|^2 },\\
\chi_{V0}(f',f) &= \left( \frac{ \sigma_0}{A_{ef\!f}^V} \right) \left( \frac{\Gamma}{4 \Delta_{f,f'}} \right)=\frac{\Gamma_V^{1D}}{\Delta_{f,f'}},\quad
& A_{ef\!f}^V = \frac{1}{n_g|\mathbf{u}^*_{V}(r^\prime\!\!_\perp,\phi')|^2 }.
\end{align}

The Hamiltonian can also be rewritten as below using the Stokes operators and collective spin operators.
\begin{align}
H_{\rm eff} 
=\frac{\hbar}{\tau} \Big\{ & \left[ \big( \chi_{H,\uparrow} + \chi_{H,\downarrow}\big) + \big(\chi_{V,\uparrow} + \chi_{V,\downarrow}\big) \right] \hat{J}_0 \hat{S}_0 \nonumber \\
+ & \left[ \big( \chi_{H, \uparrow} + \chi_{H,\downarrow}\big) - \big( \chi_{V,\uparrow} + \chi_{V,\downarrow} \big)\right]  \hat{J}_0 \hat{S}_1 \nonumber \\
+ & \left[ \big( \chi_{H,\uparrow} - \chi_{H,\downarrow}\big) + \big(\chi_{V,\uparrow} - \chi_{V,\downarrow} \big) \right] \hat{J}_z \hat{S}_0 \nonumber \\
+ & \left[ \big( \chi_{H,\uparrow} - \chi_{H,\downarrow}\big) - \big(\chi_{V,\uparrow} - \chi_{V,\downarrow} \big) \right]  \hat{J}_z \hat{S}_1\Big\}
\end{align}
The first term is an overall scalar shift and thus does not contribute to the relative dynamics.  The second term is a constant birefringence and can be canceled with a compensating waveplate as long as the atom number remains constant which is usually the case when the trapping time is fairly large compared to the measurement time. The first two terms can be also be canceled when we have the detuning approximately equally biased for the $ f=3 $ and $ f=4 $ ground states. 
For example, we  can choose $ \Delta_3=-4.6 $ GHz and $ \Delta_4=4.6 $ GHz to the $ 6P_{1/2} $ excited state sublevels to satisfy this condition, where the hyperfine splitting of the excited state can be ignored ($ ~500 $ MHz) compared to the detuning. However, we would like to leave the choice of detuning to control the third and fourth terms as will be discussed consequently. 

The final term describes the QND Faraday interaction we wish to isolate (similar to the Faraday interaction since we choose to use the $ x $-axis as the quantization axis), but this requires dealing with the third term that describes the effect of the scalar light shift on the rotation of the pseudo-spin.  Canceling the third term amounts to enforcing the condition that
	\begin{align}
		\chi_{H,\uparrow} - \chi_{H,\downarrow} = \chi_{V,\downarrow} - \chi_{V,\uparrow} ,
	\end{align}
which can be satisfied if we carefully choose the detuning of the probe light. The wavelength to choose to cancel the third term is atom position related, since the condition is determined by the effective mode areas which may have different ratios for the $ H $ and $ V $ modes at different locals. We can the exact wavelength to satisfy this condition as the \textit{magic wavelength}\index{magic wavelength}. If this condition can be met, then we can achieve an interaction of the form,
	\begin{align}
		H_{\rm eff} = \frac{\hbar}{\tau} \chi_{\rm eff} \hat{J}_z \hat{S}_1
	\end{align}
where $\chi_{\rm eff} = 2(\chi_{H,\uparrow} - \chi_{H,\downarrow})$.  

Using this, we can prepare the spins in $ D $ state on the Bloch sphere and characterize the collective spin state along the $ z $-axis after the rotation along $ S_1 $ axis due to the photon-atom interaction. To achieve this, we use the $ \hat{S}_3 $ Stokes vector component measurement. As a result of the backaction of the polarization measurement, there is a squeezing to the collective spin state which results in a reduced uncertainty of measurement output. To see this, we assume the photon number is large and apply the Holstein-Primakoff approximation to set $ \hat{S}_1=\sqrt{\frac{N_L}{2}}\hat{P}_L $ and $ \hat{S}_3=\sqrt{\frac{N_L}{2}}\hat{X}_L $. Now the effective Hamiltonian can be written as
\begin{align}
H_{\rm eff} = \frac{\hbar}{\tau} \chi_{\rm eff} \sqrt{\frac{N_L}{2}}\hat{J}_z \hat{P}_L. 
\end{align}
The $ \hat{S}_3 $ measurement is achieved through sending the signal light to one input port of a beam splitter along as a vacuum input on the other input port and then performing a balanced Homodyne measurement of the $ X_L $ quadrature. The equivalent Kraus operator conditional on this measurement is 
\begin{align}
\hat{A}_{X_L} &= \bra{X_L} e^{-i\chi_{\rm eff} \sqrt{\frac{N_L}{2}}\hat{J}_z \hat{P}_L} \ket{0_L}\propto \exp\left\{ -\frac{\kappa T}{4}(m-\hat{J}_z)^2 \right\},
\end{align} 
where $ m=\frac{X_L}{\chi_{\rm eff} \sqrt{N_L/2}} $ is the measurement outcome in angular momentum units, and $ \kappa T=\chi_{\rm eff}^2N_L $ is the integrated measurement strength per spin. The shot noise resolution of the QND measurement is $ \sigma^2=\frac{1}{\kappa T} $. The Kraus operator is exactly the same as Equ.~\eqref{KrausOpSq} to generate a spin squeezing
 state. For a SCS input state, the output state probability distribution is given by 
\begin{align}
P_{M|m} \propto e^{-\frac{(M-\bar{M}(m))^2}{2\Delta J_{out}^2}},
\end{align}
where $ \Delta J_{out}^2 =\frac{\Delta J_{in}^2}{1+\xi}=\frac{J}{2(1+\xi)} $, $ \bar{M}(m)=\frac{m}{1+\xi} $, and $ \xi\equiv \frac{\Delta J_{in}^2}{\sigma^2}=\frac{J}{2\sigma^2}=\frac{\chi_{e\!f\!f}^2}{4}N_AN_L $ is the measurement strength which characterizes the measurement backaction and the squeezing effect. The ability to resolve the initial quantum variance of $ J_z $ within the resolution of the meter is the key to QND squeezing.




\subsection{Birefringence and Faraday spectroscopies}

\textcolor{blue}{Discuss the homodyne detection and sensitivity to the atom number and operating frequency in the shot noise limit.  It relates to (i) the phase shift and (ii) the shot noise resolution of the polarimeter. Should cover expectation value and fluctuation measurements.}

For the birefringence measurement of the clock states discussed above, the fluctuation of the $ S_3 $ measurement is a combination effect of the shot noise fluctuation of the photon detector and the projection noise as the signal to determine the collective spin state:
\begin{align}
\Delta M^2 &= \Delta P^2_{SN} + \Delta P^2_S .
\end{align}
The smallest detectable spin polarization is determined by the shot noise limit condition that 
\begin{align}
\Delta P_S = \Delta P_{SN},
\end{align}
where the standard variance of the signal can be estimated by
\begin{align}
\Delta P_S=P_0 \sin(\varphi_{_N}) \approx P_0 \varphi_{_N}
\end{align}
and the shot noise variance is determined by
\begin{align}
\Delta P_{SN} = \sqrt{\frac{P_0 \hbar \omega_0 }{2\eta \tau_{pd}}}.
\end{align}
We estimate the phase difference is
We estimate the phase difference is
\begin{align}
\varphi_{_N} &= N_A \chi_{e\!f\!f}=N_A [(\chi_{H,\uparrow}-\chi_{H,\downarrow})-(\chi_{V,\uparrow}-\chi_{V,\downarrow})]\\
&= 2N_AC_{j'}^{(0)}(\Gamma_{H}^{1D}-\Gamma_V^{1D})\frac{1}{\Delta}=\frac{C_{j'}^{(0)}\sigma_0\Gamma_{vac}}{2}(\frac{1}{A^H_{e\!f\!f}}-\frac{1}{A^V_{e\!f\!f}})\frac{1}{\Delta}\\
&=N_AC_{j'}^{(0)}n_g\sigma_0\frac{\Gamma_{vac}}{2\Delta}\left[| \mathbf{u}_H(r'_{\!\perp})|^2- | \mathbf{u}_V(r'_{\!\perp})|^2 \right],
\end{align}
where $\frac{1}{\Delta}=\frac{1}{2}\sum_{f'}(\frac{1}{\Delta_{f',4}}-\frac{1}{\Delta_{f',3}})\approx \frac{1}{\Delta_{f',4}}$.

Now, we consider the critical case: $\eta =100\%$ and $\tau_{pd} = \frac{1}{\gamma_s}$, where the photon scattering rate
\begin{align}
\gamma_s &= \sigma(\Delta) \frac{I(\br')}{\hbar \omega_0} \\
\sigma(\Delta) &=\frac{\sigma_0}{1+\frac{4\Delta^2}{\Gamma^2_{vac}}}\approx \sigma_0 \frac{\Gamma_{vac}^2}{4\Delta^2} \quad \text{(far detuning.)}
\end{align}
We can rewrite 
\begin{align}
\Delta P_{SN} &=P_0\sqrt{\frac{ \sigma_0 }{2A_{in}}}\frac{\Gamma_{vac}}{2\Delta},\\
\Delta P_S &= N_A C_{j'}^{(0)}P_0 \frac{\sigma_0}{A_{e\!f\!f}}\frac{\Gamma_{vac}}{2\Delta}, 
\end{align}
with the effective mode areas
\begin{align}
A_{in } &= \frac{P_0}{I(\br')}=\frac{2}{| \mathbf{u}_H(r'_{\!\perp})|^2+ | \mathbf{u}_V(r'_{\!\perp})|^2},\\
A_{e\!f\!f} &= \frac{1}{n_g\left[ | \mathbf{u}_H(r'_{\!\perp})|^2- | \mathbf{u}_V(r'_{\!\perp})|^2\right]}.
\end{align}
Therefore, the $ \Delta P_S = \Delta P_{SN}$ condition gives the resolution of the birefringence measurement in terms of the minimum atom number as
\begin{align}
N^{min}_A &= \frac{1}{C_{j'}^{(0)}}\sqrt{\frac{A_{e\!f\!f}^2}{A_{in}\sigma_0}}.
\end{align}

\subsection{Other applications?} 


\section{Discussions}

\subsection{Connect to the Heisenberg picture}
Quantization of field. Input-output formalism
\begin{align}
\hat{a}_{out} &= f(\hat{a}_{in}).
\end{align}
Connection to the dyadic Green function.

Phase shift expression. 

\subsection{Connect to the Schrodinger picture}




%\subsection{Group velocity}

\subsection{Achievable phase shift with scalar atomic polarizabilities}

\textcolor{blue}{Show the phase shift and the decay rate is a result of the interference between the free dipole radiation and the reflection from the nanofiber interface. Discuss the phase shift control landscape and the difference with the vacuum case.}
\begin{align}
\delta\phi &= -\frac{\Gamma_{1D}^\mu}{2\Delta},\\
\frac{\Gamma_{1D}^\mu}{\Gamma_0} &= \frac{6\pi c}{\omega}\frac{\sum_g\mathbf{d}_{eg}\cdot \mathrm{Im}\left[\mathbf{G}_g^\mu(\br',\br') \right]\cdot\mathbf{d}_{eg}^* }{\sum_g|\mathbf{d}_{eg}|^2} = 1+ \frac{3}{2} \frac{\mathrm{Im}\left[\sum_g\mathbf{d}_{eg}^*\cdot \mathbf{E}^{(R,\mu)}_g(\br') \right]}{\sum_g|\mathbf{d}_{eg}|^2 k^3}\nonumber\\
&=\frac{3\pi}{2}\left(\frac{c}{\omega}\right)^2\frac{c}{v_g} \frac{\sum_{g}|\mathbf{d}_{eg}\cdot \mathbf{u}^\mu(\br')|^2}{\sum_g|\mathbf{d}_{eg}|^2}\\
\mathbf{E}^{(R,\mu)}_g(\br') &= -\frac{1}{4\pi k^2} \mathbf{G}^{(R,\mu)}_g(\br',\br')\cdot \mathbf{d}_{eg}.
\end{align}
The index $ R $ indicates the reflected component, and $\mu=(m,f,\beta)  $ identifies the normalized fiber mode $ \mathbf{u}^\mu(\br') $. 

We can write 
\begin{align}
\Gamma_{vac} &= \frac{4\omega_0^3|\mathbf{d}|^2}{3\hbar c^3}=-\frac{8\pi \omega_0^2}{\hbar c^2}\left[ \mathbf{d}\cdot \mathrm{Im}[\mathbin{\color{red}{\mathbf{G}^{(0)}}}(\br',\br')]\cdot \mathbf{d}^* \right]\\
\Gamma &= -\frac{8\pi \omega_0^2}{\hbar c^2}\left[ \mathbf{d}\cdot \mathrm{Im}[\mathbf{G}(\br',\br')]\cdot \mathbf{d}^* \right]=-\frac{8\pi \omega_0^2}{\hbar c^2}\left[ \mathbf{d}\cdot \mathrm{Im}[\mathbin{\color{red}{\mathbf{G}^{(0)}}}(\br',\br')+\mathbin{\color{red}{\mathbf{G}^{(R)}}}(\br'\br')]\cdot \mathbf{d}^* \right]\\
\end{align}
The decay rate is result of the interference between the free dipole radiation and the reflection from the nanofiber interface.

\begin{align}
\Gamma &\propto -\mathbf{d}\cdot \mathrm{Im}[\mathbf{G}(\br',\br')]\cdot \mathbf{d}^* \\
&=\mathrm{tr}\left[ \mathbin{\color{red}{(\mathbf{d}^*\mathbf{d})}}\cdot\mathbin{\color{blue}{ \mathrm{Im}[\mathbf{G}^*(\br',\br')]}}  \right]\\
&= \mathrm{tr}\left[ \boldsymbol{\rho} \cdot \mathrm{Im}[\mathbf{G}^{*}(\br',\br')]  \right]\ge 0
\end{align}
where $\boldsymbol{\rho}=(\mathbf{d}^*\mathbf{d})$ is defined as the dipole orientation tensor which is merely a property of the atoms. The dyadic Green function part is only a property of the waveguide.  

By mathematical definition, $\mathrm{Im}[\mathbf{G}^{*}(\br',\br')]$ is positive definite. 
\begin{align}
\mathrm{Im}[\mathbf{G}^{*}(\br',\br')] &= \sum_{i=1,2,3} \mathbin{\color{red}{g_i}}\hat{\mathbf{v}}_i\hat{\mathbf{v}}_i,\,\text{with}\, g_i>0.
\end{align}
$\hat{\mathbf{v}}_i$ form the principal axes of the decay rate. The principal axes indicate the dipole orientations along which the interference bwteen the free dipole radiation and the reflected field (equivalent to the radiation from the image dipole) is most constructive and destructive.   
\begin{align}
\Gamma &= C(\omega)\sum_i g_i(\hat{\mathbf{v}}_i\cdot \boldsymbol{\rho}\cdot \hat{\mathbf{v}}_i) 
= \sum_i \mathbin{\color{blue}{(d'_i)^2}} \mathbin{\color{red}{g_i}} \\
&= \mathbin{\color{red}{\Gamma_1}}\cos^2\phi\sin^2\theta+\mathbin{\color{red}{\Gamma_2}}\sin^2\phi\sin^2\theta+\mathbin{\color{red}{\Gamma_3}}\cos^2\theta,
\end{align}
where $ d'_i=\sqrt{\hat{\mathbf{v}}_i\cdot \boldsymbol{\rho}\cdot \hat{\mathbf{v}}_i}$ and $\mathbf{d}'=\sum_i d'_i\hat{\mathbf{v}}_i$ defines the equivalent dipole orientation of the atomic polarizability transition.

The range of decay rates:
$$\mathbin{\color{red}{\Gamma_1}}=\Gamma_{max}\mathbin{\color{red}{\ge \Gamma (\theta,\phi) \ge}} \Gamma_{min}=\mathbin{\color{red}{\Gamma_3}}$$

Quantum transitions and dipole orientations correspondence:
\begin{align}
\sigma_+ &\leftrightarrow \mathbf{d}_+\propto \frac{1}{\sqrt{2}}(i\mathbf{e}_{r\!_\perp}+\mathbf{e}_\phi)\\
\pi &\leftrightarrow \mathbf{d}_0 \propto \mathbf{e}_z\\
\sigma_- &\leftrightarrow \mathbf{d}_-\propto \frac{1}{\sqrt{2}}(-i\mathbf{e}_{r\!_\perp}+\mathbf{e}_\phi).
\end{align}
Example: completely mixed state decay rate calculation:
\begin{align}
\boldsymbol{\rho} &=\frac{1}{3}(\boldsymbol{\rho}_++\boldsymbol{\rho}_0+\boldsymbol{\rho}_-)=\frac{d_0^2}{3}\boldsymbol{I}\\
\Gamma &=\frac{C(\omega)}{3}d_0^2 \mathrm{tr}\left[ \mathrm{Im}[\mathbf{G}^*(\br',\br')] \right]=\frac{1}{3}(\Gamma_1+\Gamma_2+\Gamma_3).
\end{align}
This is equivalent to assume the dipole is uniformly pointing to any direction, and hence
$\Gamma = \int \frac{\mathrm{\Omega}}{4\pi}\Gamma(\theta,\phi)=\frac{1}{3}(\Gamma_1+\Gamma_2+\Gamma_3)$.

\textcolor{red}{Some plots here.}

The phase shift is proportional to the time integral of the path on the emission rate surface. The range of the decay rates determines the achievable phase shift in a unit time. However, the emission rate surface for the vacuum case is a uniform sphere and the corresponding phase shift in a given time is a constant independent from the orientation of the dipole with a scalar atomic polarizability. Therefore, it is possible to use the scalar atomic polarizability to realize a wide controlable phase shift range in the off-resonance regime that the vacuum configuration can hardly achieve. 


\subsection{Interference due to a one-sided or two-sided atom chain}
\textcolor{blue}{Effect of an infinite long one-side chain... S matrix, reflectivity... Random filling effect...}

\textcolor{blue}{Effect of the two-side chain:
The symmetry or antisymmetry nature (TBD) of the radiation surface at the opposite sides along the $ r\!_\perp $ axis will yield a constructive/destructive interference of the two-side chain.} 

\textcolor{blue}{There could be a polarization transformation effect for the forward or backward propagating guided modes, which has been studied in literature.} 

\section{Conclusions}

\begin{acknowledgments}
X.Q. would like to particularly thank Ninnat Dangniam, Tzu-Cheng Wu and Matthew Chase for their inspiring discussions. We thank the UNM Center for Advanced Research Computing for computational resources used in this work.
\end{acknowledgments}

\appendix
\section{Dyadic Green functions for the atom-nanofiber system}
Expressions for the 9 elements of the dyadic Green function and its reflected and transmitted decomposition.

\section{Group index of refraction of a single-mode nanofiber}
Expression of $ n_g $ for the HE11 mode.

Frequency stability.

\section{Junk: Effects of the evanescent field and the multilevel structure of the atom}
In general, 
\begin{align}
\Gamma \propto \mathbf{d}_{eg}\cdot \mathrm{Im}\left[\mathbf{G}(\br',\br') \right]\cdot\mathbf{d}_{eg}^*=\mathrm{tr}\left[\mathbf{d}_{eg}^*\mathbf{d}_{eg}\cdot \mathrm{Im}\left[\mathbf{G}(\br',\br') \right] \right]\propto \mathrm{tr}\left[\boldsymbol{\alpha}_{eg}\cdot \mathrm{Im}\left[\mathbf{G}(\br',\br') \right] \right]
\end{align}
where $ \boldsymbol{\alpha}_{eg} $ is the polarizability of the atom due to the transition between levels labeled by $ eg $. Therefore, the phase shift effect can be treated as a combination effect of the atomic internal structure and the external field properties. 

Since 
\begin{align}
\mathbf{d}_{eg}\cdot \mathrm{Im}\left[\mathbf{G}(\br',\br') \right]\cdot\mathbf{d}_{eg}^*>0
\end{align}
for a physical decay rate, $\mathrm{Im}\left[\mathbf{G}(\br',\br')\right]$ is positive definite and should always has three positive eigenvalues which indicate the range of $ \Gamma $ and phase shift at the atom position. The 3 corresponding eigenvectors indicate the 3 orthogonal principal axes of the radiation/emission surface. Case studies...

Radiation surface theory for the effective orientation of dipoles, elementary transitions ($ \pi $ and $ \sigma_\pm $ transitions) and the example of completely mixed state case. 
\begin{align}
\Gamma_{mix} &\propto \frac{1}{3} \mathrm{tr}\left[ \mathrm{Im}\left[\mathbf{G}(\br',\br')\right] \right].
\end{align}

For the atomic internal structure, we have the irreducible tensor decompositions that 
\begin{align}
\boldsymbol{\alpha}_{eg} = \boldsymbol{\alpha}^S + \boldsymbol{\alpha}^V + \boldsymbol{\alpha}^T.
\end{align}
The scalar component will yield a decay rate equivalent to the completely mixed state case. 

Another way to look at this problem is that we can decompose the guided mode Green function tensor into the scalar, vector and tensor parts as well, since it is irreducible.
\begin{align}
\mathbf{G}^g=\mathbf{G}^S+\mathbf{G}^V+\mathbf{G}^T.
\end{align}
Therefore, where the position of the atom relative to the fiber mode yields a strong scalar component, the atomic response is more independent of the atom state... 

Some interesting examples of state-dependent decay and phase shift...


%\begin{center}
%{\bf References}
%\end{center}

%\bibliography
%\bibliographystyle{amsplain}
\bibliographystyle{unsrt}
% \nocite{*}
\ifwindows
	\bibliography{F:/References/Archive/Archive}
\else
	\bibliography{/media/F/References/Archive/Archive}
\fi


\end{document}